Evaluating Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe using radiocarbon data

### 2019-05-26 article/05_Conclusion.Rmd
wording

*The main trends in the distribution of burial rites in Bronze Age Europe can be detected in bulk radiocarbon data* (Figure \ref{development_burial_type} B and \ref{development_burial_construction} B) and indeed *they allow long-term observations concerning cultural distance* (Figure \ref{sed_region_matrix}, Table \ref{tab:dacta} and Table \ref{tab:dactb} and Figure \ref{correlationtimeseries} B), although with the low amount of data currently available, *most findings should be taken with great caution* (Table \ref{tab:gprcrosstab}, Figure \ref{development_burial_type} A and \ref{development_burial_construction} A, Figure \ref{correlationtimeseries} A). In this paper sample size is effectively being ignored once proportions of burial rites are computed.

>>>>

*The main trends in the distribution of burial rites in Bronze Age Europe can be detected in bulk radiocarbon data* (Figure \ref{development_burial_type} B and \ref{development_burial_construction} B) and indeed *they allow long-term observations concerning cultural distance* (Figure \ref{sed_region_matrix}, Table \ref{tab:dacta} and \ref{tab:dactb} and Figure \ref{correlationtimeseries} B), although with the low amount of data currently available, *most findings should be taken with great caution* (Table \ref{tab:gprcrosstab}, Figure \ref{development_burial_type} A, \ref{development_burial_construction} A and \ref{correlationtimeseries} A). In this paper sample size is effectively being ignored once proportions of burial rites are computed.
